pairwise plot of flash result of flash Z-score and loading of flash on logcpm of count data

### 2017-05-03 analysis/pairwiseplotofflashgtexzscore.Rmd
Files commited by wflow_commit.

---
title: "pairwise plot of flash result of flash Z-score"
author: "Wei Wang"
date: 2017-05-01
output: html_document
---

@@

@@

```{r}
i = 1
j = 3
plot(b_flash$f[,i],b_flash$f[,j],col = "grey",pch = 16)

```

@@

>>>>

---
title: "pairwise plot of flash result of flash Z-score and loading of flash on logcpm of count data"
author: "Wei Wang"
date: 2017-05-01
output: html_document
---

@@

## pairwise loading plot of Z-score

@@

```{r}
i = 1
j = 3
plot(b_flash$f[,i],b_flash$f[,j],col = "grey",pch = 16)
plot(as.vector(b_flash$l[,i] %*% t(b_flash$f[,i])),
     as.vector(b_flash$l[,j] %*% t(b_flash$f[,j])),col = "grey",pch = 16)
```

@@

```{r}
gsvd = readRDS("../data/GTExdata/logcpm/sixpairssubsample/svd60.rds")
par(mfrow = c(3,3),mar = c(5,4,4,2)-1.8)
for(i in 1:60){
  barplot(gsvd$u[,i],col = color_six,border = color_six)
}
```
